%==============================================================================
% Home IoT Security — empirical study report
% Section skeleton mirroring the transportation IoT study
% ("On Security Vulnerabilities in Transportation IoT Devices").
% All section bodies are intentionally left blank.
%
% Build:  pdflatex home_iot_security_report.tex   (run twice for refs)
% Class:  IEEEtran (conference).
%==============================================================================
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{url}
\usepackage[hidelinks]{hyperref}

% Inline placeholder for values the author must supply. Renders in bold red.
\newcommand{\stub}[1][?]{{\color{red}\textbf{[#1]}}}

\begin{document}

\title{On Security Vulnerabilities in Home IoT Devices}

\author{
\IEEEauthorblockN{Author Name}
\IEEEauthorblockA{Affiliation\\ City, State\\ email}
}

\maketitle

%==============================================================================
\begin{abstract}

\end{abstract}

\begin{IEEEkeywords}

\end{IEEEkeywords}

%==============================================================================
\section{Introduction}
\label{sec:intro}


%==============================================================================
\section{Related Work}
\label{sec:related}


%==============================================================================
\section{Our Methodology}
\label{sec:method}

In this section, we describe the methodology used in this paper. First, we
identified the device types belonging to each home IoT category and collected
the CVEs reported about them in NVD~\cite{ref-nvd}. We collected the CVEs using
two complementary text-search methods --- a vendor/brand search and a
device-keyword search, both run offline through a single engine against one fixed
NVD snapshot --- reconciled their results per category, and further densified
coverage of confirmed devices through a CPE-based expansion step. Then, we extracted each
CVE's characteristics, including the corresponding CWEs and CVSS information.
Motivated by a previous study~\cite{ref-mcsoftware}, we grouped the individual
CWEs into the primary clusters of the CWE-888 Software Fault Patterns
view~\cite{ref-cwe888} in order to build a `big picture' of the security
vulnerabilities in home IoT devices. Finally, because keyword- and brand-based
NVD searches are text-based and therefore noisy, every candidate vulnerability
was subjected to a structured false-positive review before analysis.

The empirical work presented in this paper follows the case study (i.e.,
observational) approach based on publicly available data in NVD that are entered
and validated by experts and are widely used by researchers and practitioners.
Using an experimental approach (e.g., penetration testing) or a survey (e.g.,
collecting expert opinions) are complementary empirical approaches that are out
of the scope of this paper.

\subsection{Scope: what counts as a home IoT device}
\label{sec:method-scope}

We define a \emph{home IoT device} as an internet-connected sensor, appliance,
or embedded system deployed within a residential environment for the purpose of
monitoring, automation, or control, owned and maintained by non-expert consumers
without dedicated IT security oversight. For a device type to be in scope it must
satisfy all five definitional criteria: (1)~\emph{connectivity} --- it
communicates over a standard network protocol (TCP/IP, MQTT, CoAP, Zigbee, BLE);
(2)~\emph{device class} --- it is a special-purpose sensor, appliance, or
embedded system, not general-purpose IT (PC, phone, tablet, server, game
console); (3)~\emph{deployment context} --- it is intended for a private
residence, not primarily for enterprise or industrial use; (4)~\emph{function}
--- it qualifies if \emph{either} (a)~its primary purpose is to monitor, automate,
or control the home environment or its systems (climate, security, access,
lighting, appliances, presence), \emph{or} (b)~it serves as a home-control surface
or hub for \emph{other} home IoT devices, discovering, controlling, or displaying
their state (e.g.\ acting as a Matter/Thread controller or border router, running a
voice assistant, or surfacing camera/sensor feeds); general-purpose computing and
pure media playback with no such control role do not qualify; and
(5)~\emph{security context} --- it is owned and
maintained by consumers with no professional security administration. An
operational study-inclusion criterion further requires that the device have a
CPE-identifiable footprint in NVD and be subject to CVE disclosure. Because
connectivity (criterion~1) is satisfied by virtually every networked product, it
is the device's own function (criterion~4) and class (criterion~2) that
discriminate membership; a device that merely interoperates with home IoT is not
itself home IoT. Entertainment hardware is therefore in scope \emph{only} when it
doubles as a home-control surface under criterion~4(b): streaming TVs, sticks, and
boxes (whose platforms act as Matter/Thread controllers, run assistants, and
surface camera/doorbell feeds) and smart speakers/displays are admitted, whereas
game consoles and VR/AR headsets remain excluded as general-purpose compute that
fails criteria~2 and~4. On the networking axis the discriminator is likewise
whether a device controls other home IoT devices rather than merely carries their
traffic: IoT hubs, bridges, and Matter/Thread/Zigbee controllers are in scope,
while pure-transport gear (plain routers, modems, ONT, unmanaged switches) is
excluded and appears only as untrusted threat-model context.

The study analyzes \stub[N $=$ 24] home IoT categories: \stub[final category list:
cameras, doorbells, baby monitors, door locks, alarms, sensors, thermostats, air
conditioners, fans, air purifiers, smart plugs, lighting, refrigerators, robot
vacuums, other appliances, hubs, smart speakers, sleep trackers, shades, EV charging,
home power, garden, pet, streaming]. \stub[Note categories defined but dropped or
folded: game consoles and VR/AR headsets (general-purpose compute, out by criteria~2
and~4) and pure-transport networking such as routers and modems (out by criterion~4)
are excluded; sleep trackers remain listed but are dominated by wearables and pending
a bedside-only rebuild that may drop them. Smart displays and soundbars are folded
into the smart-speakers category, and blinds/curtains/shutters into a single shades
category.]

\subsection{CVE collection from NVD}
\label{sec:method-collect}

CVEs are publicly known security vulnerabilities reported in NVD~\cite{ref-nvd}
and attributed to specific software applications or libraries. All searches were
run offline against a single fixed snapshot of NVD, built by merging the per-year
NVD JSON feeds (\stub[year range, e.g.\ 2002--2026]) downloaded on
\stub[snapshot date]; freezing the corpus this way makes the dataset reproducible
and citeable (``as of'' that date) and removes data-lag differences between the two
searches. To maximize recall, we collected CVEs related to home IoT devices using
two complementary text-search methods, each more reliable in a different respect,
later augmented by a CPE-based expansion step:

\paragraph{Vendor/brand search} For each category we first compiled a list of
the manufacturers and brands that produce devices of that type, then searched the
snapshot for those vendor and brand names. The brand lists were assembled from
\stub[brand-list sources, e.g.\ manufacturer directories / retailer catalogues /
targeted web searches per category]; where a bare brand name overlaps unrelated
products it was qualified with a product word (e.g.\ ``carrier infinity'' rather
than ``carrier'') to suppress obvious noise. Every brand term was matched against
both the CVE \emph{description text and the CPE (Common Platform Enumeration)
strings}, so that brand-in-CPE associations are captured, using whole-word matching
(tokens must sit on alphanumeric boundaries, with a trailing plural allowed) to
block substring false hits while leaving CPE matching unaffected. Each output row
also records \emph{which} brand term(s) matched it, enabling the per-term precision
analysis in Section~\ref{sec:method-precision}. Because brand names frequently
overlap with unrelated products, this method has higher recall but is more prone to
false positives.

\paragraph{Device-keyword search} In parallel, we searched for generic device-type
phrases (e.g.\ ``ip camera'', ``video doorbell'', ``smart lock''), restricted to
device-type language only --- no brands, protocols, or firmware names, since brand
discovery is the vendor search's job. Crucially, this search is run through the
\emph{same offline engine and against the same fixed snapshot} as the vendor
search, matching \emph{both description text and CPE strings} under the same
whole-word rule and emitting the identical output schema (including matched-term
attribution). The two methods therefore differ only in their search \emph{terms}
(device phrases versus brand names), which makes their outputs directly comparable.
Each CVE carries its CVSS score and version, CWE identifiers, CPE strings, and
description.

\paragraph{Reconciliation} For each category we combined the two result sets
using set operations. The \emph{intersection} (vendor $\cap$ keyword) yields the
CVEs found by both methods. The \emph{difference} is computed \emph{bidirectionally}
into two disjoint sets: \emph{vendor-only} (vendor $-$ keyword) collects vendor CVEs
the keyword search missed, and \emph{keyword-only} (keyword $-$ vendor) collects
keyword CVEs the brand list missed, which surfaces gaps in the vendor/brand list.
Both difference sets are the primary input to the false-positive review described in
Section~\ref{sec:method-review}: reviewing them cleans the dataset and, by mining the
confirmed true matches, feeds new terms back into whichever list was missing them
(keyword phrases from vendor-only true matches, brands from keyword-only true
matches).

\paragraph{CPE expansion} As a third, recall-oriented discovery step, we densify
coverage of devices already confirmed as in scope. Seeding from the true-match
(\texttt{Yes}) rows of the review, we take each confirmed device's
\texttt{vendor:product} CPE (guarded to genuine device CPEs --- \texttt{vendor:product}
pairs whose \texttt{part} is hardware or operating system, dropping vendor-only or
shared application/library CPEs), scan the snapshot for every other CVE that NVD
attributes to that same product, and subtract everything the two text searches
already found. The remaining CVEs form a third candidate set that flows back through
the same false-positive review. This step deepens coverage of already-confirmed
products rather than introducing new brands, so its yield is category-dependent.

We collected the data from NVD from \stub[start date] until \stub[end date]. In
total, we collected \stub[total CVEs] CVEs across the \stub[N] categories.
\stub[Note any vendors deliberately excluded for ambiguity --- analogous to the
transportation study's conservative exclusion of Qualcomm chips --- e.g.\ generic
chipsets or brand names that could not be confirmed as the device in question.]

\paragraph{Comparability} An earlier iteration of this pipeline ran the keyword
search against the live NVD API (matching the description only) while the vendor
search ran offline over a year-feed snapshot (matching description plus CPE), which
made apparent ``gaps'' between the methods partly an artifact of data lag and of the
description-versus-CPE match surface rather than genuine coverage differences. We
eliminated this confound by running \emph{both} term lists through the same offline
engine against the same fixed NVD snapshot, matching description plus CPE under the
same whole-word rule, so that the only remaining difference between the two searches
is the search terms themselves.

\subsection{CWE and CVSS data extraction}
\label{sec:method-extract}

Each CVE is typically attributed to one or more CWEs. However, some CVEs did not
have enough information to be associated with a CWE in NVD, or were not in NVD's
CWE mapping; these are listed as \texttt{NVD-CWE-noinfo} and
\texttt{NVD-CWE-Other}, respectively. Out of the total \stub[total CVEs] CVEs,
\stub[N] were \texttt{NVD-CWE-noinfo} and \stub[N] were \texttt{NVD-CWE-Other}.
These \stub[N] CVEs were included in our CVE-level analysis but did not contribute
to the CWE analysis. In total, \stub[total CWEs] CWEs were associated with the
\stub[total CVEs] CVEs; these were attributed to only \stub[unique CWEs] unique
CWEs.

For each CVE we also extracted the CVSS information. CVSS scores range from 0 to
10 and are computed from the vulnerability's exploitability and impact
metrics~\cite{ref-cvss}. CVSS severity is derived from the score: a score of 0
indicates the None severity level, and the Low, Medium, High, and Critical levels
correspond to score ranges of 0.1--3.9, 4.0--6.9, 7.0--8.9, and 9.0--10,
respectively. \stub[If both CVSS v2 and v3.x scores are present in the dataset,
state which version was used when both are available.] Lastly, for each CVE we
manually extracted information about the vulnerable components from the CVEs'
descriptions \stub[(confirm whether component extraction was performed, and how
components were named/normalized)].

\subsection{Mapping individual CWEs to the CWE-888 view}
\label{sec:method-cwe888}

CWE is a community-developed taxonomy of common weaknesses maintained by
MITRE~\cite{ref-cwe}. Because the CWE hierarchy is large and complex, several
views have been developed to organize it. We chose the CWE-888 Software Fault
Patterns view~\cite{ref-cwe888} to categorize the identified CWEs for two
reasons: (i)~it was used in~\cite{ref-mcsoftware}, which allows consistency and
direct comparison of results, and (ii)~it is focused on fault categorization, is
more technical, and captures a wider range of weaknesses than alternatives such
as the CWE-699 Software Development view~\cite{ref-cwe699}. We use the most recent
version of CWE-888 and focus only on its 23 primary clusters, which we refer to
as primary vulnerability classes.

If an identified CWE is itself part of the CWE-888 view, we mapped it directly to
its corresponding primary class. If it is not, we examined its parent CWEs and
mapped those to the CWE-888 view; a CWE whose parents fall under two different
primary classes therefore counts toward both. \stub[Report the over-counting
bookkeeping for this dataset: the number (and percentage) of CVEs whose CWE
mapped to two parents, and the number of CVEs that listed two distinct CWEs and
how those resolved across primary classes.] This approach builds a more complete
picture of the types of vulnerabilities present while limiting over-counting.

\subsection{False-positive classification}
\label{sec:method-review}

Because the vendor and keyword searches are purely text-based, generic brand names
and terms produce false positives (e.g.\ a brand string that also names an
unrelated commercial product, or marketing copy that merely mentions a device
category). Each candidate CVE in the difference set was therefore independently
classified as a true match for its category or a false positive.

To make this trustworthy, every row was judged \emph{independently and blind} by
\stub[five] reviewers --- two human researchers (\stub[Reviewer A] and
\stub[Reviewer B]) and three AI reviewers (Claude Code, ChatGPT Codex, and
Google's Gemini/Gemma). Blindness is enforced structurally: each reviewer works
on its own copy of the data containing only the raw fields plus its own empty
judgment columns, so no reviewer can see another's answer. All reviewers apply a
single shared rubric \emph{and} a shared per-category scope note (a short in/out
scope statement pinned to each category), judging \emph{only} from each row's
\texttt{description} and \texttt{cpe\_strings}; pinning one scope note per category
ensures that agreement between reviewers reflects a common scope rather than three
different interpretations of a one-word category label.

Each reviewer assigns three fields per row: a \emph{Judgment} of \texttt{Yes}
(genuinely affects a home IoT device of this category), \texttt{No} (false
positive), or \texttt{Maybe} (genuinely ambiguous); a \emph{Confidence} of
\texttt{High} or \texttt{Low}; and a short, self-contained \emph{Reasoning}
required for \texttt{Low}-confidence and \texttt{Maybe} rows. A \texttt{Maybe} is
always paired with \texttt{Low} confidence. Low confidence is used when the device
is plausibly residential but primarily commercial/industrial, when the description
names the category but the CPE points at enterprise hardware, or when the CVE lies
in a software or protocol layer shared between home and non-home contexts. A
missing CPE string does not by itself force a \texttt{Maybe}: CPE data is
frequently absent on recent (2024--2026) CVEs due to NVD enrichment lag, so an
unambiguous description of a home device and a residential attack vector is
classified on its content.

Of the three AI reviewers, two (Claude Code and ChatGPT Codex) are run manually and
the third (Gemini/Gemma) is scripted against the vendor's API; all three judge the
combined review set for a category, which unions the vendor-only, keyword-only, and
CPE-expansion directions (a \texttt{Difference Type} field on each row records its
origin). Their judgments are then merged. A row is flagged for human adjudication
when \stub[the human-review condition: both strong reviewers (Claude and Codex) are
Low confidence, or the three AI judgments are not unanimous]. Gemini is treated as a
weaker third vote: its judgment counts toward unanimity, but its self-reported
confidence is recorded and excluded from the flag. A human then adjudicates only the
flagged rows, and each CVE's judgments are folded into a single final label
(\texttt{ai-consensus} for unflagged rows, \texttt{human} for adjudicated rows). All
settled judgments are written to a persistent store keyed by (category, CVE); when a
difference set is later regenerated after a term-list change, prior judgments are
restored automatically and only genuinely new rows are re-reviewed, so no settled
work is repeated. \stub[Report the outcome of the review --- e.g.\ the false-positive
rate per category, the number of rows flagged for human review, and inter-reviewer
agreement.]

\subsection{Term-level precision and list refinement}
\label{sec:method-precision}

The matched-term attribution recorded at collection lets us close the quality loop
from the precision side as well. Joining each settled final judgment back to the
term(s) that pulled its CVE into the corpus, we compute a per-term precision --- the
fraction of a term's judged difference-set matches that were confirmed true --- for
every brand and keyword term. Terms that fall at or below a low precision threshold
over a minimum number of judged rows (\stub[e.g.\ $\le 0.10$ over $\ge 5$ rows]) are
flagged as prune candidates: a brand string colliding with unrelated software, or an
over-broad vendor entry pulling in generic hardware, becomes a concrete line item to
remove from the term list rather than a recurring disagreement to re-adjudicate.
Because the settled labels cover only the difference set, this is a prioritized prune
list (per-term precision \emph{on the difference set}), not a global precision over
all of a term's matches.

\subsection{Recall estimation}
\label{sec:method-recall}

Because no single search recovers every relevant CVE, we estimate combined recall
using capture--recapture. Treating the vendor search ($V$) and keyword search ($K$)
as two capture occasions of the same underlying CVE population, we compute the
Chapman estimator $\hat{N}$ of the total population per category (with a log-normal
95\% confidence interval) and report combined recall as $|V \cup K| / \hat{N}$.
Because $V$ and $K$ are positively dependent --- a CVE naming both a brand and a
device phrase is more likely to be caught by both --- the two-source estimator is
biased downward, so this recall is an upper bound. We therefore also fit an
AIC-selected Poisson log-linear model over three capture sets, $V$, $K$, and the full
CPE-expansion set $C$, which can accommodate pairwise dependence, with a bootstrap
confidence interval. Categories in which one list is a subset of the other yield a
degenerate recall of $1.0$ and are excluded from the pooled cross-category total.
This estimation is read-only --- the recall counterpart to the review's precision ---
and changes nothing in the dataset.

%==============================================================================
\section{RQ1: Analysis of Vulnerability Classes in Home IoT Devices}
\label{sec:rq1}


\subsection{}
\label{sec:rq1-cat1}


\subsection{}
\label{sec:rq1-cat2}


\subsection{}
\label{sec:rq1-cat3}


\subsection{}
\label{sec:rq1-cat4}


%==============================================================================
\section{RQ2: Analysis of CVSS Scores and Severity}
\label{sec:rq2}

In this section we analyze the CVSS scores and severity levels of the confirmed
home IoT device CVEs, summarized in Table~\ref{tab:cvss-summary}. The CVSS score
ranges from 0 to 10 and is a composite metric that integrates the exploitability
and impact of a vulnerability, combined with temporal and environmental
factors~\cite{ref-cvss}. Severity is derived from the score using the standard
qualitative bands described in Section~\ref{sec:method-extract}.

As shown in Table~\ref{tab:cvss-summary}, among the 16 categories with at least
five scored CVEs the highest median CVSS score was found in \texttt{alarms}
(median~8.8, mean~8.21, $n=77$), followed by \texttt{hub} (8.2, 8.09, $n=90$) and
a three-way tie at 8.1 among \texttt{doorlock}, \texttt{home-power}, and
\texttt{garden}. The lowest median was \texttt{babymonitor} (7.2, 6.94, $n=7$),
followed by a tie at 7.4 between \texttt{robotvacuum} and \texttt{pet}. We
conducted a Kruskal-Wallis test across these 16 categories and obtained
$H=77.454$ ($df=15$), $p=2.03\times10^{-10}$, rejecting the null hypothesis that
there is no statistically significant difference among the CVSS scores of the
categories. Four categories --- \texttt{fridge}, \texttt{sensors},
\texttt{appliances}, and \texttt{airconditioner} --- had fewer than five scored
CVEs ($n \le 3$ each) and were excluded from the test; they are reported
descriptively in Table~\ref{tab:cvss-summary} (marked~$\dagger$), but no
statistical conclusion should be drawn from them individually.

The results of Dunn's post-hoc test (rank-based, tie-corrected, two-sided,
Bonferroni-adjusted across all $\binom{16}{2}=120$ pairwise comparisons) showed
that \texttt{streaming} --- by far the largest category by CVE count
($n=2{,}081$) --- had significantly lower CVSS scores than \texttt{alarms}
($p_{\text{bonf}}=6.3\times10^{-6}$), \texttt{hub}
($p_{\text{bonf}}=2.2\times10^{-5}$), and \texttt{cameras}
($p_{\text{bonf}}=4.5\times10^{-3}$). \texttt{alarms} additionally scored
significantly higher than \texttt{robotvacuum} ($p_{\text{bonf}}=0.025$) and
\texttt{cameras} ($p_{\text{bonf}}=0.049$). No other pairs among the 16 tested
categories differed significantly after correction; the full $120$-pair table is
available in the accompanying data release
(Section~\ref{sec:conclusion:data-availability}).

\texttt{alarms} had both the highest mean CVSS score (8.21) among categories with
$n \ge 5$ and the highest critical-severity share of any large category (46.8\%
of its 77 CVEs), consistent with home security/alarm sensors and hubs being
frequent, high-impact targets. \texttt{streaming}, despite dominating the corpus
by CVE count, had a comparatively low critical share (6.4\%) and a majority of
its scores clustered in the High band (55.2\%); \texttt{lighting} showed the
opposite pattern --- the highest concentration in the High band of any category
(62.1\%) but one of the lowest critical shares (6.9\%). \texttt{robotvacuum} and
\texttt{babymonitor} had the lowest mean scores (6.80 and 6.94, respectively),
and neither reported a Critical-severity CVE among its scored CVEs.

Unlike the transportation IoT study, which manually extracted the most
vulnerable \emph{components} (e.g.\ web interface, RKE system, infotainment
system) from each CVE description and cross-tabulated them against severity (its
Table~IV), this study has not yet performed an analogous component-level
extraction. \stub[A component-level breakdown, mirroring Table~IV of the
transportation study, is left as future work (Section~\ref{sec:lessons}) and
would let us test whether specific attack surfaces --- e.g.\ companion mobile
apps, cloud APIs, or physical Zigbee/BLE radio stacks --- concentrate the
Critical/High-severity vulnerabilities the way RKE and web-interface components
did in that study.]

\begin{table*}[t]
\centering
\caption{CVSS score distribution and severity shares for confirmed home IoT
device CVEs, by category. $N$ is the confirmed-\texttt{Yes} CVE count (severity
percentages are of $N$, including any unscored CVEs); Mean/Median/Std are
computed over the subset with a CVSS score. Categories marked $\dagger$ had
$< 5$ scored CVEs and were excluded from the Kruskal-Wallis/Dunn's tests.}
\label{tab:cvss-summary}
\scriptsize
\begin{tabular}{lrrrrrrrr}
\toprule
Category & $N$ & Mean & Median & Std & Critical\% & High\% & Medium\% & Low\% \\
\midrule
doorlock        & 17    & 7.71 & 8.1  & 1.19 & 11.8 & 47.1 & 29.4 & --   \\
smartspeakers   & 31    & 7.46 & 7.6  & 1.88 & 19.4 & 32.3 & 45.2 & 3.2  \\
doorbell        & 23    & 7.86 & 7.5  & 1.44 & 30.4 & 47.8 & 21.7 & --   \\
thermostat      & 8     & 7.94 & 7.85 & 1.82 & 37.5 & 37.5 & 25.0 & --   \\
babymonitor     & 7     & 6.94 & 7.2  & 0.71 & --   & 71.4 & 28.6 & --   \\
smartplugs      & 32    & 7.46 & 7.5  & 1.68 & 21.9 & 37.5 & 40.6 & --   \\
alarms          & 77    & 8.21 & 8.8  & 1.91 & 46.8 & 27.3 & 24.7 & 1.3  \\
robotvacuum     & 23    & 6.80 & 7.4  & 2.05 & 13.0 & 52.2 & 17.4 & 13.0 \\
fridge$\dagger$ & 3     & 7.95 & 7.95 & 2.62 & 33.3 & --   & 33.3 & --   \\
sensors$\dagger$& 2     & 9.10 & 9.1  & 0.00 & 50.0 & --   & --   & --   \\
lighting        & 29    & 7.59 & 7.9  & 1.20 & 6.9  & 62.1 & 31.0 & --   \\
appliances$\dagger$& 3 & 8.13 & 8.1  & 1.65 & 33.3 & 33.3 & 33.3 & --   \\
hub             & 92    & 8.09 & 8.2  & 1.64 & 27.2 & 51.1 & 18.5 & 1.1  \\
ev-charging     & 24    & 7.32 & 7.65 & 1.50 & --   & 58.3 & 41.7 & --   \\
home-power      & 31    & 7.98 & 8.1  & 1.79 & 38.7 & 32.3 & 25.8 & 3.2  \\
garden          & 17    & 7.68 & 8.1  & 2.26 & 35.3 & 35.3 & 17.6 & 11.8 \\
pet             & 29    & 7.12 & 7.4  & 2.25 & 27.6 & 24.1 & 41.4 & 6.9  \\
streaming       & 2{,}081 & 7.25 & 7.8 & 1.56 & 6.4  & 55.2 & 35.9 & 2.5  \\
airconditioner$\dagger$& 1 & 6.30 & 6.3 & 0.00 & --   & --   & 100.0& --   \\
cameras         & 555   & 7.72 & 7.7  & 1.48 & 19.3 & 51.4 & 24.3 & 0.7  \\
\bottomrule
\end{tabular}
\end{table*}

%==============================================================================
\section{Threats to Validity}
\label{sec:threats}

\subsection{Construct Validity}
\label{sec:threats-construct}

Our operationalization of ``home IoT device'' rests on five definitional criteria
(Section~\ref{sec:method-scope}) that require judgment calls at the margin --- e.g.\
whether a streaming device's platform genuinely acts as a home-control surface, or
whether a brand's product line is residential versus commercial/industrial. We
mitigated this by freezing the category list before large-scale collection and by
pinning a shared, written scope note per category (\texttt{category\_scope.csv}) that
every reviewer, human or AI, judges against, but the underlying category boundaries
are themselves a modeling choice and a different set of criteria could redraw them.
Mapping individual CWEs onto the CWE-888 Software Fault Pattern clusters
(Section~\ref{sec:method-cwe888}) is a second construct-validity threat: when a CWE is
not itself in CWE-888, we map through its parent CWEs, and a CWE whose parents span two
primary clusters is counted in both, which can inflate cluster totals relative to a
stricter one-CWE-one-cluster scheme. We follow the same mapping convention as prior
work~\cite{ref-mcsoftware} to keep the two studies comparable, but the choice of view
(CWE-888 over, e.g., CWE-699) and the parent-resolution rule are both choices that
shape the resulting ``big picture'' of vulnerability classes.

\subsection{Internal Validity}
\label{sec:threats-internal}

The vendor and keyword searches are text-based over CVE descriptions and CPE strings,
so classification errors in either direction are possible: a generic brand name can
collide with an unrelated product (per-term precision analysis, Section~\ref{sec:method-precision},
found \stub[34] of 176 judged terms at or below the 0.10-precision prune threshold,
e.g.\ vendor terms that matched only unrelated enterprise products in every judged row),
and a device-relevant CVE can fail to contain any of our search terms at all. We
addressed the first failure mode with the three-AI-plus-human review of every
difference-set row and with the term-precision pass that flags terms for pruning; we
addressed the second, partially, with the CPE-expansion step (Section~\ref{sec:method-collect}),
which finds additional CVEs attributed to already-confirmed device products
independent of description wording. \stub[As of this writing, the review is not yet
complete: N=991 difference-set rows remain unreviewed (\texttt{Final Source = pending})
and only 20 of 1{,}011 human-flagged rows have been adjudicated by both human
reviewers; update this paragraph, and any false-positive-rate or inter-reviewer
agreement figures reported in Section~\ref{sec:method-review}, once review finalizes.]
Reviewer disagreement is itself a threat: Codex is systematically more conservative
(rejecting unfamiliar security-focused brands) and Gemini/Gemma is systematically more
liberal (accepting function-overlap across categories, e.g.\ IP camera $\to$ baby
monitor); we treat Gemini as the weaker third vote and exclude its confidence from the
human-review flag for this reason, but its judgment still counts toward the unanimity
check, so residual bias from either model can still shape which rows are, and are not,
escalated to a human.

\subsection{External Validity}
\label{sec:threats-external}

Our dataset is bounded by NVD's CVE disclosure and CPE-tagging practices, not by actual
real-world deployment or exploitation. A device with no publicly disclosed CVE is
invisible to this study regardless of how insecure it may be in practice, and smaller or
newer vendors are structurally under-represented relative to established brands with
active CVE reporting histories and abundant CPE coverage. CPE data is also known to lag
on recent (2024--2026) CVEs (Section~\ref{sec:method-review}), so the most recent portion
of the corpus is more likely to be classified from description text alone. Because the
snapshot is a single fixed point in time (\stub[2026-06-25]), any vulnerability disclosed
after that date is out of scope by construction, and the study reports a static
``as-of'' picture rather than a continuously updated one. Finally, our capture--recapture
recall estimates (Section~\ref{sec:method-recall}) are so far only available for
\stub[2 of 24] categories (cameras: recall $\approx 0.55$; alarms: recall $\approx 0.27$,
both derived from the two-source Chapman estimator), and even the completed estimates are
biased downward by the positive dependence between the vendor and keyword searches (a CVE
naming both a brand and a device phrase is more likely to be caught by both), so the true
combined recall is likely higher than these figures suggest, and generalizing them to the
remaining categories should be done cautiously until the estimator is run at scale.

\subsection{Reliability}
\label{sec:threats-reliability}

To support reproducibility, all searches run against one fixed, dated, and documented
NVD snapshot (Section~\ref{sec:method-collect}) rather than the live NVD API, so the
corpus a reader would reconstruct today matches the one analyzed here. Every
difference-set judgment, human or AI, is persisted in a store keyed by
(category, CVE), so the review can be audited, re-run, or extended without silently
losing or duplicating prior work. The one part of the pipeline that is not fully
deterministic is the Gemini/Gemma reviewer, whose free-tier model
(\stub[\texttt{gemma-4-31b-it}]) may be swapped or updated over time; we mitigate this by
keeping one model fixed across an entire review pass and recording which model produced
each Gemini judgment.

%==============================================================================
\section{Lessons Learned and Implications}
\label{sec:lessons}


%==============================================================================
\section{Conclusions}
\label{sec:conclusion}


%==============================================================================
\section*{Data Availability}
\label{sec:conclusion:data-availability}

The scripts and derived datasets supporting this study are available at
\stub[repository URL / DOI]. The repository includes: the vendor/brand and keyword term
lists used for collection (\texttt{vendor\_terms.csv}, \texttt{keyword\_terms.csv}); the
raw per-category search outputs (\texttt{results\_all\_<category>.xlsx},
\texttt{keyword\_<category>.csv}); the offline search engine and pipeline scripts (CVE
collection, set reconciliation, CPE expansion, review generation and merging, term-precision,
and recall estimation); the shared classification rubric and per-category scope notes used
by every reviewer (\texttt{CLASSIFICATION\_PROMPT.md}, \texttt{category\_scope.csv}); the
blind per-reviewer judgment files and their merged, human-adjudicated, and finalized outputs
for every category; and the persistent judgment store keyed by (category, CVE) that backs
the entire review process. The one artifact not tracked in the repository is the bulk NVD
snapshot itself (\texttt{nvd\_all.csv}, \stub[360{,}981] CVE records merged from the NVD 2.0
API as of \stub[2026-06-25]), which is excluded for size rather than for access reasons; the
snapshot's provenance and exact rebuild procedure are documented in
\texttt{data/nvd-snapshot/SNAPSHOT.md} so that it can be regenerated in full from public NVD
data. \stub[State any additional restrictions, e.g.\ whether the repository is public at
publication time or shared upon request, and whether an API key is required to rebuild the
snapshot (NVD and Gemini/Gemma keys are read from a local, gitignored \texttt{.env} and are
not themselves part of the dataset).]

%==============================================================================
\begin{thebibliography}{00}
\bibitem{ref-nvd} NIST, ``National Vulnerability Database (NVD),''
  \url{https://nvd.nist.gov/}.
\bibitem{ref-mcsoftware} K. Goseva-Popstojanova and J. Tyo, ``Experience report:
  Security vulnerability profiles of mission critical software: Empirical
  analysis of security related bug reports,'' in \emph{IEEE 28th Int. Symp. on
  Software Reliability Engineering (ISSRE)}, 2017, pp.~152--163.
\bibitem{ref-cwe888} Common Weakness Enumeration, ``CWE-888: Software Fault
  Pattern (SFP) Clusters,''
  \url{https://cwe.mitre.org/data/definitions/888.html}.
\bibitem{ref-cwe699} Common Weakness Enumeration, ``CWE-699: Software
  Development,'' \url{https://cwe.mitre.org/data/definitions/699.html}.
\bibitem{ref-cwe} Common Weakness Enumeration, ``CWE,''
  \url{https://cwe.mitre.org/data/index.html}.
\bibitem{ref-cvss} FIRST, ``Common Vulnerability Scoring System (CVSS):
  Specification Document,'' \url{https://www.first.org/cvss/}.
\end{thebibliography}

\end{document}
